Sparse Representation Approaches for First Stage Retrieval: A Review

### 2021-12-14 src/article.tex
Fix typo.

    \paragraph{Training the gating controller.}
    Consider a passage-query/summary parallel corpus \emph{C}, which contains passage \emph{p}, the
    cor- responding target text \emph{t}, and the binary bag-of-words vector of \emph{t} (\emph{T}).
    In order to maximize probability values of all terms in vocabulary, binary cross-entropy loss
    is used, which has the following form:
    \begin{equation}
        L_{exp}=-\lambda_1\sum_{j \in \{m|T_m=0\}}log(1-G_j)-\lambda_2\sum_{k \in \{m|T_m=1\}}logG_k
    \end{equation}
    where $\lambda_1$ and $\lambda_2$ are tunable hyper-parameters, first is for terms expected not to be
    expanded, second one is for terms that appear in the target text, and \emph{G} is is the dense
    gating probability distribution for \emph{p} \cite{SparTerm}.\\\par
    Thus, SparTerm provides a function that is used to map the frequency-based and bag-of-words
    representation to a sparse term importance distribution in the whole vocabulary.
    This model also has limitation: since the gating mechanism is learned in advance, this prevents
    the model from learn the optimal sparsification strategy for the ranking task.

>>>>

    \paragraph{Training the gating controller.}
    Consider a passage-query/summary parallel corpus \emph{C}, which contains passage \emph{p}, the
    corresponding target text \emph{t}, and the binary bag-of-words vector of \emph{t} (\emph{T}).
    In order to maximize probability values of all terms in vocabulary, binary cross-entropy loss
    is used, which has the following form:
    \begin{equation}
        L_{exp}=-\lambda_1\sum_{j \in \{m|T_m=0\}}log(1-G_j)-\lambda_2\sum_{k \in \{m|T_m=1\}}logG_k
    \end{equation}
    where $\lambda_1$ and $\lambda_2$ are tunable hyper-parameters, first is for terms expected not to be
    expanded, second one is for terms that appear in the target text, and \emph{G} is is the dense
    gating probability distribution for \emph{p} \cite{SparTerm}.\\\par
    Thus, SparTerm provides a function that is used to map the frequency-based and bag-of-words
    representation to a sparse term importance distribution in the whole vocabulary.
    This model also has limitation: since the gating mechanism is learned in advance, this prevents
    the model from learn the optimal sparsification strategy for the ranking task.
